Project 2

### 2021-10-14 project_2.Rmd
Final HTML

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
library(sentimentr)
library(ggiraphExtra)
library(ggplot2)
library(RColorBrewer)
library(scales)
```

@@

ggRadar(
  data = sentiment_both,
  mapping = aes(color = author),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

@@

p<-ggplot(data=combined_table, aes(x=percent, y=title, fill=author)) +
  geom_bar(stat="identity")
p
```

```{r exporting_tables}
save(author_table, hemingway_corpus, fitzgerald_corpus, file = "saved_data.rda")
```

>>>>

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)
library(readtext)
library(sentimentr)
library(ggiraphExtra)
library(ggplot2)
library(RColorBrewer)
library(scales)
library(plotly)
library(htmlwidgets)
```

@@

data_vis_2 <- ggRadar(
  data = sentiment_both,
  mapping = aes(color = author),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

@@

data_vis_1 <-ggplot(data=combined_table, aes(x=percent, y=title, fill=author, text = paste("% of emotion: ", percent, sep = ""))) +
  geom_bar(stat="identity") + labs(x = "% of emotion detected", 
       y = "All novels", fill = "Author", title = "Emotive content in all novels")

data_vis_1_int <- ggplotly(data_vis_1, tooltip = "text")
data_vis_1_int
```

```{r exporting_tables}
save(author_table, hemingway_corpus, fitzgerald_corpus, data_vis_1_int, data_vis_2, file = "saved_data.rda")
```
